VM-Centric Snapshot Deduplication for Converged Cloud Architectures

### 2014-07-19 snapshot_system/paper_dedup.tex
re

\item 
\textbf{VM-centric file system block management} --
When a chunk is not detected as a duplicate to any existing chunk, this chunk will be written
into a file system block.  
In addition to the fact that a distributed file system block is often
configured to be much  larger than a chunk, a number of chunks can be combined together
and compressed further using a standard compression method such as LZO. 
Thus a  backend file system block contains a large number of compressed chunks.
%We manage this accumulation process using a log-structured storage scheme built
%on a distributed file system discussed in Section~\ref{sect:architecture}.
%Non-PDS chunks from the same VM are stored in one append store. 
We set the following two constraints in composing chunks for a file system block:
1) Each file system block is either dedicated to non-PDS chunks, or to PDS-chunks.
2) A non-PDS file system block is only associated with one VM.

Restricting the association with one VM improves fault isolation when some file blocks are lost during 
storage failures. 
In addition, storing PDS chunks separately from non-PDS chunks
allows special replication handling for those popular shared data. 
%%% talk something about snapshot store advantage here? %%%
%One could try to rely on filesystem features to 
If we do not separate the
popular chunks from the less-popular, the popular chunks are dispersed across
all of the filesystem blocks in the storage system and we would have
to add extra replications for {\em all} file blocks in order to   follow the popularity-driven replication idea 
from ~\cite{Reliability06}. That reduces the storage efficiency.
%Then we cannot leverage the file system features to 
%provide extra replication to popular and shared chunks because  
%we have to add extra replication to each file block as long as it contains a popular chunk.

@@

%The system allows all machines conduct backups in parallel, and each machine
%conducts the backup of one VM at a time, and thus only requires a write buffer for one VM.
\end{itemize}

>>>>

\item 
\textbf{VM-centric file system block management} --
When a chunk is not detected as a duplicate to any existing chunk, this chunk will be written
into a file system block.  
In addition to the fact that a distributed file system block~\cite{googlefs03,hdfs10} is often
configured to be much  larger than a chunk, a number of chunks can be combined together
and compressed further using a standard compression method such as LZO. 
Thus a  backend file system block contains a large number of compressed chunks.
%We manage this accumulation process using a log-structured storage scheme built
%on a distributed file system discussed in Section~\ref{sect:architecture}.
%Non-PDS chunks from the same VM are stored in one append store. 
We set the following two constraints in composing chunks for a file system block:
1) Each file system block is either dedicated to non-PDS chunks, or to PDS-chunks.
2) A non-PDS file system block is only associated with one VM.

Restricting the association with one VM improves fault isolation when some file blocks are lost during 
storage failures. 
In addition, storing PDS chunks separately from non-PDS chunks
allows special replication handling for those popular shared data. 
%%% talk something about snapshot store advantage here? %%%
%One could try to rely on filesystem features to 
If we do not separate the
popular chunks from the less-popular, the popular chunks are dispersed across
all of the filesystem blocks in the storage system and we would have
to add extra replications for {\em all} file blocks in order to   follow the popularity-driven replication idea 
from ~\cite{Reliability06}. That reduces the storage efficiency.

%and compare

%Then we cannot leverage the file system features to 
%provide extra replication to popular and shared chunks because  
%we have to add extra replication to each file block as long as it contains a popular chunk.

@@

%The system allows all machines conduct backups in parallel, and each machine
%conducts the backup of one VM at a time, and thus only requires a write buffer for one VM.
\end{itemize}
The underlying distributed  file system has  a fixed replication degree for 
all file system blocks~\cite{googlefs03,hdfs10}.
We add extra replicas for file blocks containing PDS chunks  
and this brings additional  failure protection for these chunks shared by many VMs.
Appendix~\ref{sect:fault} provides a detailed analysis of snapshot availability
under this VC scheme and compares it with VO.
